Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-09-12 files/Chapter7/Introduction.tex
Introduction chapter 6

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin plate model when used in application. Validity in this context refers to how well the solutions of a model compare to the solutions of a more realistic, higher-dimensional model.

@@

Section 7.2 is a discussion and a verification of numerical results of the work done in \cite{LVV09} In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. We also include some extra results for different values of the parameter $\alpha$.

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{Introduction}
This chapter is an investigation into the validity of a cantilever Timoshenko beam and a cantilever Reissner-Mindlin. Validity in this context refers to how well the solutions of a model compare to the solutions of a more realistic, higher-dimensional model. The application of the models are limited to beam-type and plate-type problems.

@@

Section 7.2 is a discussion and a replication of numerical results of the work done in the article \cite{LVV09}. In this article, the authors compare a cantilever Timoshenko beam to a cantilever two-dimensional beam. Extra results are included in this section to verify the conclusions of the authors of \cite{LVV09}. The results of this section are also used as a reference for the rest of the chapter.
